A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
some recs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@959 43ef1190-90fd-4dd7-a769-d0121f02b80e

\todo{ref kasei on mtime}.

>>>>

Based on the results of DyLDO, it is highly likely that most cache
prohibitions are misguided, and server administrators are adviced to
turn them off unless they are sure they are required.

Data owners should seek to understand their change frequency, and
adjust cache headers accordingly. Framework authors should make it
easy to set the expected lifetime, and manage changes to the
publishing schedule.

To allow generation and validation of \httph{Last-Modified} and
\httph{ETag} headers, DBMS authors should make sure it is much cheaper
to retrieve the modification time of any subgraph, than to retrieve
the subgraph itself. This would be a great improvement for
RFC7232-based caching, when revalidation is required. It would also
help simple heuristic based caching.\todo{ref kasei on mtime}.
